### 2025-09-17 paper/sec/authoring-workflow.tex
Fig. 4 caption.

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.50\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow-correct}
        \caption{Author Acceptance workflow}
        \label{fig:data-flow-correct}
    \end{subfigure}\hfill
    \begin{subfigure}{0.50\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow-error}
        \caption{Author Rejection workflow}
        \label{fig:dataflow-error}
    \end{subfigure}
    \caption{Two possible paths through the basic editing loop. In Fig.~\ref{fig:data-flow-correct}, the
    author accepts the generated expression after interactively verifying its correctness. In
    Fig.~\ref{fig:dataflow-error}, the author identifies an error (the expression mentions accuracy, while the
    article highlights timing) and rejects it.}
    \label{fig:overall-architecture}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.50\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow-correct}
        \caption{Author Acceptance workflow}
        \label{fig:data-flow-correct}
    \end{subfigure}\hfill
    \begin{subfigure}{0.50\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/data-flow-error}
        \caption{Author Rejection workflow}
        \label{fig:dataflow-error}
    \end{subfigure}
    \caption{Two possible paths through the basic editing loop: (a) author accepts generated expression after
    interactively verifying its correctness; (b) author rejects proposed expression, having identified an
    error (natural language mentions accuracy, while interaction reveals use of timing data).}
    \label{fig:overall-architecture}
\end{figure}
